Topological Equivariant Artist Model for Visualization Library Architecture

### 2022-09-09 paper/main.tex
summary table

>>>>

\section{Objects & Functions}
This table contains a summary of the topological structures introduced in \autoref{sec:atct:fiber-bundles} and \autoref{sec:construction:vtotal} and what they encode. These structures serve as the basis of abstractions for the data objects in \autoref{sec:discussion}.

\begin{table}[h]
  \centering
  \begin{tabular}{|r|r|r|r|r|}
    \hline\\
   & Data  & Visual  & Graphic  & Encodes \\
\hline \\
\textcolor{total}{total space} & \dtotal & \vtotal & \gtotal &  \\
\hline\\
\textcolor{base}{base space} & \dbase & \dbase & \gbase & topological structure\\
\hline \\ 
\textcolor{base}{open set} & \openset & \openset & \opensetg & subspace \\
\hline \\
\textcolor{fiber}{fiber space} & \dfiber & \vfiber & \gfiber  & field structure\\
\hline \\
\textcolor{section}{Section} & \dsection & \vsection & \gsection & data set \\
\hline
  \end{tabular}
\end{table}

This table contains a summary of the functions introduced in \autoref{sec:atct:xi}, \autoref{sec:artist}, and \autoref{sec:construction}. These functions are an abstraction of the behavior implemented in visualization libraries.
